---
title: "FUT2_dietguthealth_fiber"
author: "Yasmine"
date: "`r Sys.Date()`"
output: html_document
---

Purpose: determine associations between secretor status, fiber intake and GI inflammation marker levels. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```

```{r import}

# Genotyping 
fut2 <- read.csv("/Users/yasmine.bouzid/Documents/FUT2_analysis/data/forR_fut2.csv", header = T)

# Gut health 

df_l <- read.csv("/Users/yasmine.bouzid/Documents/GitHub/diet_guthealth/data/df_l.csv", header = T)

# MEEEERGE 


df_l <- merge(df_l, fut2, by = "subject_id") # n = 338

# unfortunately, need to correct structure of some variables each time -->


df_l$subject_id <- as.factor(as.character(df_l$subject_id))
df_l$sex <- df_l$sex %>% recode_factor('1' = 'Male', '2' = "Female")
df_l$age_cat <- df_l$age_cat %>% recode_factor('1' = '18-33.99 years', '2' = "34-49.99 years", '3' = "50-65 years")
df_l$bmi_cat <- df_l$bmi_cat %>% recode_factor('1' = 'Normal', '2' = "Overweight", '3' = "Obese")
df_l$secr_status <- as.factor(as.character(df_l$secr_status))

```

Models used for analysis: regression of transformed GI inflammation marker ~ dietary component
Note: Age, sex, BMI not included as covariates because not significantly associated with calprotectin and MPO levels. Sex included for neopterin outcome. Sex and BMI included for LBP outcome. Associations previously established. 

GIM ~ fiber + FUT2 + fiber:FUT2 + age + sex + BMI

```{r asa24-total-fiber}

# Create fibe_pk (pk = per 1000 kcal)

df_l$fibe_pk <- df_l$fibe/(df_l$kcal/1000)

# Boxplot

fig_box1 <- ggplot(df_l, aes(x=secr_status, y=fibe_pk)) + 
  geom_boxplot(notch = TRUE, 
               outlier.colour="red", 
               outlier.shape=8,
               outlier.size=4) + 
  stat_summary(fun.y=mean, geom="point", shape=23, size=6) +
  labs(
    title = "Boxplot: Fiber Intake by Secretor Status",
    x = "Secretor Status", 
    y = "Recent Fiber Intake (grams/1000 kcal)"
  ) +
  scale_x_discrete(
    labels = c("Non-secretors (n = 70)", "Secretors (n = 268)")) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 20),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14)) 
  
ggsave("/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fig_box1.jpeg", plot = fig_box1, width = 8, height = 6, units = "in")

```
Next, we'll look at total fiber from FFQ (dt_fibe)

```{r ffq-total-fiber}

# Create dt_fibe_pk (pk = per 1000 kcal)

df_l$dt_fibe_pk <- df_l$dt_fibe/(df_l$dt_kcal/1000)

# Boxplot

fig_box2 <- ggplot(df_l, aes(x=secr_status, y=dt_fibe_pk)) + 
  geom_boxplot(notch = TRUE, 
               outlier.colour="red", 
               outlier.shape=8,
               outlier.size=4) + 
  stat_summary(fun.y=mean, geom="point", shape=23, size=6) +
  labs(
    title = "Boxplot: Fiber Intake by Secretor Status",
    x = "Secretor Status", 
    y = "Habitual Fiber Intake (grams/1000 kcal)"
  ) +
  scale_x_discrete(
    labels = c("Non-secretors (n = 70)", "Secretors (n = 268)")) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 20),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14)) 
  
ggsave("/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fig_box2.jpeg", plot = fig_box2, width = 8, height = 6, units = "in")

```

Last, we'll look at soluble fiber from the FFQ (dt_fiber_sol)

```{r ffq-sol-fiber}


# Create dt_fiber_sol_pk (pk = per 1000 kcal)

df_l$dt_fiber_sol_pk <- df_l$dt_fiber_sol/(df_l$dt_kcal/1000)

# Boxplot 

fig_box3 <- ggplot(df_l, aes(x=secr_status, y=dt_fiber_sol_pk)) + 
  geom_boxplot(notch = TRUE, 
               outlier.colour="red", 
               outlier.shape=8,
               outlier.size=4) + 
  stat_summary(fun.y=mean, geom="point", shape=23, size=6) +
  labs(
    title = "Boxplot: Fiber Intake by Secretor Status",
    x = "Secretor Status", 
    y = "Habitual Soluble Fiber Intake (grams/1000 kcal)"
  ) +
  scale_x_discrete(
    labels = c("Non-secretors (n = 70)", "Secretors (n = 268)")) +
  theme_bw() +
  theme(
    plot.title = element_text(size = 20),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14)) 
  
ggsave("/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fig_box3.jpeg", plot = fig_box3, width = 8, height = 6, units = "in")

# Grid and save 




```

**Summary of Findings**: 

1. Recent fiber intake: For calprotectin model, secretor status significant and interaction between fiber and secretor status significant 
2. Habitual fiber intake: same as above 
3. Habitual soluble fiber intake: for BOTH clpn and MPO, secretor status significant and interaction between fiber and secretor status significant 
