---
title: "FUT2_dietguthealth_fiber"
author: "Yasmine"
date: "`r Sys.Date()`"
output: html_document
---

Purpose: determine associations between secretor status, fiber intake and GI inflammation marker levels. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)

```

```{r import}

# Genotyping 
fut2 <- read.csv("/Users/yasmine.bouzid/Documents/FUT2_analysis/data/forR_fut2.csv", header = T)

# Gut health 
df_c <- read.csv("/Users/yasmine.bouzid/Documents/GitHub/diet_guthealth/data/df_c.csv", header = T)

df_m <- read.csv("/Users/yasmine.bouzid/Documents/GitHub/diet_guthealth/data/df_m.csv", header = T)

df_n <- read.csv("/Users/yasmine.bouzid/Documents/GitHub/diet_guthealth/data/df_n.csv", header = T)

df_l <- read.csv("/Users/yasmine.bouzid/Documents/GitHub/diet_guthealth/data/df_l.csv", header = T)

# MEEEERGE 

df_c <- merge(df_c, fut2, by = "subject_id") # n = 288
df_m <- merge(df_m, fut2, by = "subject_id") # n = 288
df_n <- merge(df_n, fut2, by = "subject_id") # n = 282
df_l <- merge(df_l, fut2, by = "subject_id") # n = 338

# unfortunately, need to correct structure of some variables each time -->

df_c$subject_id <- as.factor(as.character(df_c$subject_id))
df_c$sex <- df_c$sex %>% recode_factor('1' = 'Male', '2' = "Female")
df_c$age_cat <- df_c$age_cat %>% recode_factor('1' = '18-33.99 years', '2' = "34-49.99 years", '3' = "50-65 years")
df_c$bmi_cat <- df_c$bmi_cat %>% recode_factor('1' = 'Normal', '2' = "Overweight", '3' = "Obese")

df_m$subject_id <- as.factor(as.character(df_m$subject_id))
df_m$sex <- df_m$sex %>% recode_factor('1' = 'Male', '2' = "Female")
df_m$age_cat <- df_m$age_cat %>% recode_factor('1' = '18-33.99 years', '2' = "34-49.99 years", '3' = "50-65 years")
df_m$bmi_cat <- df_m$bmi_cat %>% recode_factor('1' = 'Normal', '2' = "Overweight", '3' = "Obese")

df_n$subject_id <- as.factor(as.character(df_n$subject_id))
df_n$sex <- df_n$sex %>% recode_factor('1' = 'Male', '2' = "Female")
df_n$age_cat <- df_n$age_cat %>% recode_factor('1' = '18-33.99 years', '2' = "34-49.99 years", '3' = "50-65 years")
df_n$bmi_cat <- df_n$bmi_cat %>% recode_factor('1' = 'Normal', '2' = "Overweight", '3' = "Obese")

df_l$subject_id <- as.factor(as.character(df_l$subject_id))
df_l$sex <- df_l$sex %>% recode_factor('1' = 'Male', '2' = "Female")
df_l$age_cat <- df_l$age_cat %>% recode_factor('1' = '18-33.99 years', '2' = "34-49.99 years", '3' = "50-65 years")
df_l$bmi_cat <- df_l$bmi_cat %>% recode_factor('1' = 'Normal', '2' = "Overweight", '3' = "Obese")

```

Models used for analysis: regression of transformed GI inflammation marker ~ dietary component
Note: Age, sex, BMI not included as covariates because not significantly associated with calprotectin and MPO levels. Sex included for neopterin outcome. Sex and BMI included for LBP outcome. Associations previously established. 

GIM ~ fiber + FUT2 + fiber:FUT2 + age + sex + BMI

```{r asa24-total-fiber}

# Create fibe_pk (pk = per 1000 kcal)

df_c$fibe_pk <- df_c$fibe/(df_c$kcal/1000)
df_m$fibe_pk <- df_m$fibe/(df_m$kcal/1000)
df_n$fibe_pk <- df_n$fibe/(df_n$kcal/1000)
df_l$fibe_pk <- df_l$fibe/(df_l$kcal/1000)

# Calprotectin

mod_fibe_pk_c <- lm(clpn_ln ~ fibe_pk + secr_status + fibe_pk * secr_status, data = df_c)
summary(mod_fibe_pk_c) # 

# Myeloperoxidase

mod_fibe_pk_m <- lm(mpo_ln ~ fibe_pk + secr_status+ fibe_pk * secr_status, data = df_m)
summary(mod_fibe_pk_m) # 

# Neopterin

mod_fibe_pk_n <- lm(nptn_boxcox ~ fibe_pk + secr_status + fibe_pk * secr_status + sex, data = df_n)
summary(mod_fibe_pk_n) #

# LBP

mod_fibe_pk_l <- lm(lbp_ln ~ fibe_pk + secr_status + fibe_pk * secr_status + sex + bmi_final, data = df_l)
summary(mod_fibe_pk_l) # 


```
Next, we'll look at total fiber from FFQ (dt_fibe)

```{r ffq-total-fiber}

# Create dt_fibe_pk (pk = per 1000 kcal)

df_c$dt_fibe_pk <- df_c$dt_fibe/(df_c$kcal/1000)
df_m$dt_fibe_pk <- df_m$dt_fibe/(df_m$kcal/1000)
df_n$dt_fibe_pk <- df_n$dt_fibe/(df_n$kcal/1000)
df_l$dt_fibe_pk <- df_l$dt_fibe/(df_l$kcal/1000)

# Calprotectin

mod_dt_fibe_pk_c <- lm(clpn_ln ~ dt_fibe_pk + secr_status + dt_fibe_pk * secr_status, data = df_c)
summary(mod_dt_fibe_pk_c) # NS

# Myeloperoxidase

mod_dt_fibe_pk_m <- lm(mpo_ln ~ dt_fibe_pk + secr_status + dt_fibe_pk * secr_status, data = df_m)
summary(mod_dt_fibe_pk_m) # NS

# Neopterin

mod_dt_fibe_pk_n <- lm(nptn_boxcox ~ dt_fibe_pk + secr_status + dt_fibe_pk * secr_status + sex, data = df_n)
summary(mod_dt_fibe_pk_n) # NS

# LBP

mod_dt_fibe_pk_l <- lm(lbp_ln ~ dt_fibe_pk + secr_status + dt_fibe_pk * secr_status + sex + bmi_final, data = df_l)
summary(mod_dt_fibe_pk_l) # NS


```

Last, we'll look at soluble fiber from the FFQ (dt_fiber_sol)

```{r ffq-sol-fiber}


# Create dt_fiber_sol_pk (pk = per 1000 kcal)

df_c$dt_fiber_sol_pk <- df_c$dt_fiber_sol/(df_c$kcal/1000)
df_m$dt_fiber_sol_pk <- df_m$dt_fiber_sol/(df_m$kcal/1000)
df_n$dt_fiber_sol_pk <- df_n$dt_fiber_sol/(df_n$kcal/1000)
df_l$dt_fiber_sol_pk <- df_l$dt_fiber_sol/(df_l$kcal/1000)

# Calprotectin

mod_dt_fiber_sol_pk_c <- lm(clpn_ln ~ dt_fiber_sol_pk + secr_status + dt_fiber_sol_pk * secr_status, data = df_c)
summary(mod_dt_fiber_sol_pk_c) #

# Myeloperoxidase

mod_dt_fiber_sol_pk_m <- lm(mpo_ln ~ dt_fiber_sol_pk + secr_status + dt_fiber_sol_pk * secr_status, data = df_m)
summary(mod_dt_fiber_sol_pk_m) # NS

# Neopterin

mod_dt_fiber_sol_pk_n <- lm(nptn_boxcox ~ dt_fiber_sol_pk + secr_status + dt_fiber_sol_pk * secr_status + sex, data = df_n)
summary(mod_dt_fiber_sol_pk_n) # NS

# LBP

mod_dt_fiber_sol_pk_l <- lm(lbp_ln ~ dt_fiber_sol_pk + secr_status + dt_fiber_sol_pk * secr_status + sex + bmi_final, data = df_l)
summary(mod_dt_fiber_sol_pk_l) # NS


```

**Summary of Findings**: 

1. Recent fiber intake: For calprotectin model, secretor status significant and interaction between fiber and secretor status significant 
2. Habitual fiber intake: same as above 
3. Habitual soluble fiber intake: for BOTH clpn and MPO, secretor status significant and interaction between fiber and secretor status significant 
