---
title: "FUT2_dietguthealth_fiber"
author: "Yasmine"
date: "`r Sys.Date()`"
output: html_document
---

Purpose: determine associations between secretor status, fiber intake and GI inflammation marker levels. and PLOT

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggpubr)
library(rstatix)

```

```{r import}

# Genotyping 
fut2 <- read.csv("/Users/yasmine.bouzid/Documents/FUT2_analysis/data/forR_fut2.csv", header = T)

# Gut health 
df_c <- read.csv("/Users/yasmine.bouzid/Documents/GitHub/diet_guthealth/data/df_c.csv", header = T)

df_m <- read.csv("/Users/yasmine.bouzid/Documents/GitHub/diet_guthealth/data/df_m.csv", header = T)

df_l <- read.csv("/Users/yasmine.bouzid/Documents/GitHub/diet_guthealth/data/df_l.csv", header = T)

# MEEEERGE 

df_c <- merge(df_c, fut2, by = "subject_id") # n = 288
df_m <- merge(df_m, fut2, by = "subject_id") # n = 288
df_l <- merge(df_l, fut2, by = "subject_id") # n = 338

# unfortunately, need to correct structure of some variables each time -->

df_c$subject_id <- as.factor(as.character(df_c$subject_id))
df_c$sex <- df_c$sex %>% recode_factor('1' = 'Male', '2' = "Female")
df_c$age_cat <- df_c$age_cat %>% recode_factor('1' = '18-33.99 years', '2' = "34-49.99 years", '3' = "50-65 years")
df_c$bmi_cat <- df_c$bmi_cat %>% recode_factor('1' = 'Normal', '2' = "Overweight", '3' = "Obese")
df_c$secr_status <- as.factor(as.character(df_c$secr_status))

df_m$subject_id <- as.factor(as.character(df_m$subject_id))
df_m$sex <- df_m$sex %>% recode_factor('1' = 'Male', '2' = "Female")
df_m$age_cat <- df_m$age_cat %>% recode_factor('1' = '18-33.99 years', '2' = "34-49.99 years", '3' = "50-65 years")
df_m$bmi_cat <- df_m$bmi_cat %>% recode_factor('1' = 'Normal', '2' = "Overweight", '3' = "Obese")
df_m$secr_status <- as.factor(as.character(df_m$secr_status))

df_l$subject_id <- as.factor(as.character(df_l$subject_id))
df_l$sex <- df_l$sex %>% recode_factor('1' = 'Male', '2' = "Female")
df_l$age_cat <- df_l$age_cat %>% recode_factor('1' = '18-33.99 years', '2' = "34-49.99 years", '3' = "50-65 years")
df_l$bmi_cat <- df_l$bmi_cat %>% recode_factor('1' = 'Normal', '2' = "Overweight", '3' = "Obese")
df_l$secr_status <- as.factor(as.character(df_l$secr_status))

# Create fibe_pk (pk = per 1000 kcal) ASA24

df_c$fibe_pk <- df_c$fibe/(df_c$kcal/1000)
df_m$fibe_pk <- df_m$fibe/(df_m$kcal/1000)
df_l$fibe_pk <- df_l$fibe/(df_l$kcal/1000)

# Create dt_fibe_pk (pk = per 1000 kcal) FFQ

df_c$dt_fibe_pk <- df_c$dt_fibe/(df_c$dt_kcal/1000)
df_m$dt_fibe_pk <- df_m$dt_fibe/(df_m$dt_kcal/1000)
df_l$dt_fibe_pk <- df_l$dt_fibe/(df_l$dt_kcal/1000)

# Create dt_fiber_sol_pk (pk = per 1000 kcal) FFQ 

df_c$dt_fiber_sol_pk <- df_c$dt_fiber_sol/(df_c$dt_kcal/1000)
df_m$dt_fiber_sol_pk <- df_m$dt_fiber_sol/(df_m$dt_kcal/1000)
df_l$dt_fiber_sol_pk <- df_l$dt_fiber_sol/(df_l$dt_kcal/1000)

```

```{r remove-outliers1}

# separating the two secretor status levels, to eliminate outliers from each
df_c_ns <- df_c[df_c$secr_status == "non_secretor", ]
df_c_s <- df_c[df_c$secr_status == "secretor", ]

# identify and remove outliers 
out_c_ns <- boxplot.stats(df_c_ns$fibe_pk)$out # success! well..this shows the values
# df_out_c_ns <- which(df_c_ns$fibe_pk %in% c(out_c_ns)) screeee

View(identify_outliers(data = df_c_ns, variable = "fibe_pk")) # alright, I'll remove 6053 and 8031 subject_id == c(6053, 8031)

View(identify_outliers(data = df_c_s, variable = "fibe_pk")) # c(6032, 7116, 8085, 9035, 9056)

# filter out le outliers
df_c_ns_out <- df_c_ns %>% filter(!subject_id %in% c(6053, 8031)) # woop
df_c_s_out <- df_c_s %>% filter(!subject_id %in% c(6032, 7116, 8085, 9035, 9056))

# smack em back together so you can run the models .. scree I'm gonna need to do this again for the others. 

df_c_out <- rbind(df_c_ns_out, df_c_s_out) # yee
```


Models used for analysis: regression of transformed GI inflammation marker ~ dietary component
Note: Age, sex, BMI not included as covariates because not significantly associated with calprotectin and MPO levels. Sex included for neopterin outcome. Sex and BMI included for LBP outcome. Associations previously established. 

GIM ~ fiber + FUT2 + fiber:FUT2 + age + sex + BMI

```{r asa24-total-fiber}

# Calprotectin

mod_fibe_pk_c <- lm(clpn_ln ~ fibe_pk + secr_status + fibe_pk * secr_status, data = df_c_out)
summary(mod_fibe_pk_c) # 

# Plot with both genotypes 
# New facet label names for dose variable
secr.labs <- c("Non-secretors (n = 58)", "Secretors (n = 223)")
names(secr.labs) <- c("non_secretor", "secretor")

# Adding a label for statistical analysis results 
analysis_results <- "Secretor Status: β = 1.08, P = 0.005, \n Interaction (Fiber:Secretor Status): β = -0.10, P = 0.003"

# Add a new column to indicate whether each observation belongs to the facet you want to label
df_c_out$facet_label <- ifelse(df_c_out$secr_status == "secretor", TRUE, FALSE)

#annotations <- data.frame(
 # x = c(30),  # X coordinate for the annotation
  #y = c(6),   # Y coordinate for the annotation
#  label = analysis_results  # Text label for the annotation
#)

fut2fib_c1 <- ggplot(data = df_c_out, aes(x = fibe_pk, y = clpn_ln)) +
        geom_point(color = "black") +
        geom_smooth(method = "lm", 
                    se = T, 
                    color = "blue") +
  facet_grid(~secr_status,
             labeller = labeller(secr_status = secr.labs)) +
        labs(title = "Calprotectin ~ Recent Fiber + Secretor Status + Recent Fiber * Secretor Status",
             x = "Recent Fiber Intake (grams/1000 kcal)",
             y = "Transformed Calprotectin (ln(x + 3))",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 18),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 16),
           axis.text = element_text(size = 14),
        legend.position = "none",
        plot.margin = margin(10, 50, 10, 30, unit = "pt")) + 
 geom_text(data = subset(df_c_out, facet_label == TRUE), aes(x = 3.5, y = 6.5, label = analysis_results), size = 4.5, color = "black", hjust = 0)


ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_c1_out.jpg', plot = fut2fib_c1, device = 'jpeg', dpi = 300, width = 15, height = 6.25, units = "in")


```

```{r remove-outliers2}

# separating the two secretor status levels, to eliminate outliers from each
df_c_ns <- df_c[df_c$secr_status == "non_secretor", ]
df_c_s <- df_c[df_c$secr_status == "secretor", ]

# identify and remove outliers 
# out_c_ns <- boxplot.stats(df_c_ns$fibe_pk)$out # success! well..this shows the values
# df_out_c_ns <- which(df_c_ns$fibe_pk %in% c(out_c_ns)) screeee

# here's where we change the variable we're looking at (FFQ fiber)
View(identify_outliers(data = df_c_ns, variable = "dt_fibe_pk")) # alright, I'll remove 6003, 6053, 8031

View(identify_outliers(data = df_c_s, variable = "dt_fibe_pk")) # 5048, 6032, 7043, 8058

# filter out le outliers
df_c_ns_out <- df_c_ns %>% filter(!subject_id %in% c(6003, 6053, 8031)) # woop
df_c_s_out <- df_c_s %>% filter(!subject_id %in% c(5048, 6032, 7043, 8058))

# smack em back together so you can run the models .. scree I'm gonna need to do this again for the others. 

df_c_out <- rbind(df_c_ns_out, df_c_s_out) # yee
```

Next, we'll look at total fiber from FFQ (dt_fibe)

```{r ffq-total-fiber}

# Calprotectin

mod_dt_fibe_pk_c <- lm(clpn_ln ~ dt_fibe_pk + secr_status + dt_fibe_pk * secr_status, data = df_c_out)
summary(mod_dt_fibe_pk_c) # NS

# Plot with both genotypes 
# New facet label names for dose variable
secr.labs <- c("Non-secretors (n = 57)", "Secretors (n = 224)")
names(secr.labs) <- c("non_secretor", "secretor")

# Adding a label for statistical analysis results 
analysis_results <- "Secretor Status: β = 1.49, P = 0.003, \n Interaction (Fiber:Secretor Status): β = -0.13, P = 0.002"

# Add a new column to indicate whether each observation belongs to the facet you want to label
df_c_out$facet_label <- ifelse(df_c_out$secr_status == "secretor", TRUE, FALSE)

# Plot with both genotypes 

fut2fib_c2 <- ggplot(data = df_c_out, aes(x = dt_fibe_pk, y = clpn_ln)) +
        geom_point(color = "black") +
        geom_smooth(method = "lm", 
                    se = T, 
                    color = "blue") +
  facet_grid(~secr_status,
        labeller = labeller(secr_status = secr.labs)) +
        labs(title = "Calprotectin ~ Habitual Fiber + Secretor Status + Habitual Fiber * Secretor Status",
             x = "Habitual Fiber Intake (grams/1000 kcal)",
             y = "Transformed Calprotectin (ln(x + 3))",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 18),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 16),
           axis.text = element_text(size = 14),
        legend.position = "none",
        plot.margin = margin(10, 50, 10, 30, unit = "pt")) + 
 geom_text(data = subset(df_c_out, facet_label == TRUE), aes(x = 6, y = 6.5, label = analysis_results), size = 4.5, color = "black", hjust = 0)

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_c2_out.jpg', plot = fut2fib_c2, device = 'jpeg', dpi = 300, width = 15, height = 6.25, units = "in")

```

Last, we'll look at soluble fiber from the FFQ (dt_fiber_sol)

```{r remove-outliers3}

# separating the two secretor status levels, to eliminate outliers from each
df_c_ns <- df_c[df_c$secr_status == "non_secretor", ]
df_c_s <- df_c[df_c$secr_status == "secretor", ]

# identify and remove outliers 
# out_c_ns <- boxplot.stats(df_c_ns$fibe_pk)$out # success! well..this shows the values
# df_out_c_ns <- which(df_c_ns$fibe_pk %in% c(out_c_ns)) screeee

# here's where we change the variable we're looking at (FFQ fiber)
View(identify_outliers(data = df_c_ns, variable = "dt_fiber_sol_pk")) # 6003, 8031

View(identify_outliers(data = df_c_s, variable = "dt_fiber_sol_pk")) # 5048, 6032, 9035

# filter out le outliers
df_c_ns_out <- df_c_ns %>% filter(!subject_id %in% c(6003, 8031)) # woop
df_c_s_out <- df_c_s %>% filter(!subject_id %in% c(5048, 6032, 9035))

# smack em back together so you can run the models .. scree I'm gonna need to do this again for the others. 

df_c_out <- rbind(df_c_ns_out, df_c_s_out) # yee

# MPOOO

# separating the two secretor status levels, to eliminate outliers from each
df_m_ns <- df_m[df_m$secr_status == "non_secretor", ]
df_m_s <- df_m[df_m$secr_status == "secretor", ]

# identify and remove outliers 
# out_c_ns <- boxplot.stats(df_m_ns$fibe_pk)$out # success! well..this shows the values
# df_out_c_ns <- which(df_m_ns$fibe_pk %in% c(out_c_ns)) screeee

# here's where we change the variable we're looking at (FFQ fiber)
View(identify_outliers(data = df_m_ns, variable = "dt_fiber_sol_pk")) # 

View(identify_outliers(data = df_m_s, variable = "dt_fiber_sol_pk")) # 

# filter out le outliers
df_m_ns_out <- df_m_ns %>% filter(!subject_id %in% c(6003, 8031)) # woop
df_m_s_out <- df_m_s %>% filter(!subject_id %in% c(5048, 6032, 9035))

# smack em back together so you can run the models .. scree I'm gonna need to do this again for the others. 

df_m_out <- rbind(df_m_ns_out, df_m_s_out) # yee


```

```{r ffq-sol-fiber}

# Calprotectin

mod_dt_fiber_sol_pk_c <- lm(clpn_ln ~ dt_fiber_sol_pk + secr_status + dt_fiber_sol_pk * secr_status, data = df_c_out)
summary(mod_dt_fiber_sol_pk_c) #

# Plot with both genotypes 
# New facet label names for dose variable
secr.labs <- c("Non-secretors (n = 58)", "Secretors (n = 225)")
names(secr.labs) <- c("non_secretor", "secretor")

# Adding a label for statistical analysis results 
analysis_results <- "Secretor Status: β = 1.28, P = 0.01, \n Interaction (Fiber:Secretor Status): β = -0.39, P = 0.009"

# Add a new column to indicate whether each observation belongs to the facet you want to label
df_c_out$facet_label <- ifelse(df_c_out$secr_status == "secretor", TRUE, FALSE)

# Plot with both genotypes 

fut2fib_c3 <- ggplot(data = df_c_out, aes(x = dt_fiber_sol_pk, y = clpn_ln)) +
        geom_point(color = "black") +
        geom_smooth(method = "lm", 
                    se = T, 
                    color = "blue") +
  facet_grid(~secr_status,
        labeller = labeller(secr_status = secr.labs)) +
        labs(title = "Calprotectin ~ Habitual Soluble Fiber + Secretor Status + Habitual Sol. Fiber * Secretor Status",
             x = "Habitual Soluble Fiber Intake (grams/1000 kcal)",
             y = "Transformed Calprotectin (ln(x + 3))",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 18),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 16),
           axis.text = element_text(size = 14),
        legend.position = "none",
        plot.margin = margin(10, 50, 10, 30, unit = "pt")) + 
 geom_text(data = subset(df_c_out, facet_label == TRUE), aes(x = 2.25, y = 6.5, label = analysis_results), size = 4.5, color = "black", hjust = 0)

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_c3_out.jpg', plot = fut2fib_c3, device = 'jpeg', dpi = 300, width = 15, height = 6.25, units = "in")

# Myeloperoxidase

mod_dt_fiber_sol_pk_m <- lm(mpo_ln ~ dt_fiber_sol_pk + secr_status + dt_fiber_sol_pk * secr_status, data = df_m_out)
summary(mod_dt_fiber_sol_pk_m) # riiiiight so now that's NS

# Plot with both genotypes 
# New facet label names for dose variable
secr.labs <- c("Non-secretors (n = 58)", "Secretors (n = 225)")
names(secr.labs) <- c("non_secretor", "secretor")

# Adding a label for statistical analysis results 
# analysis_results <- "Secretor Status: β = 0.89, P = 0.02, \n Interaction (Fiber:Secretor Status): β = -0.24, P = 0.03"

# Add a new column to indicate whether each observation belongs to the facet you want to label
# df_m_out$facet_label <- ifelse(df_m_out$secr_status == "secretor", TRUE, FALSE)

# Plot with both genotypes 

fut2fib_m3 <- ggplot(data = df_m_out, aes(x = dt_fiber_sol_pk, y = mpo_ln)) +
           geom_point(color = "black") +
        geom_smooth(method = "lm", 
                    se = T, 
                    color = "blue") +
  facet_grid(~secr_status,
        labeller = labeller(secr_status = secr.labs)) +
        labs(title = "Myeloperoxidase ~ Habitual Soluble Fiber + Secretor Status + Habitual Sol. Fiber * Secretor Status",
             x = "Habitual Soluble Fiber Intake (grams/1000 kcal)",
             y = "Transformed Myeloperoxidase (ln(x + 1))",
             fill = "Secretor Status") +
  theme_bw() + 
theme(text = element_text(size = 18),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 16),
           axis.text = element_text(size = 14),
        legend.position = "none",
        plot.margin = margin(10, 50, 10, 30, unit = "pt")) 
# geom_text(data = subset(df_m_out, facet_label == TRUE), aes(x = 2, y = 9, label = analysis_results), size = 4.5, color = "black", hjust = 0)

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_m3_out.jpg', plot = fut2fib_m3, device = 'jpeg', dpi = 300, width = 15, height = 6.25, units = "in") # I CRY


```


```{r remove-outliers4}

# LBP tot fib
# separating the two secretor status levels, to eliminate outliers from each
df_l_ns <- df_l[df_l$secr_status == "non_secretor", ]
df_l_s <- df_l[df_l$secr_status == "secretor", ]

# identify and remove outliers 
# out_c_ns <- boxplot.stats(df_l_ns$fibe_pk)$out # success! well..this shows the values
# df_out_c_ns <- which(df_l_ns$fibe_pk %in% c(out_c_ns)) screeee

# here's where we change the variable we're looking at (FFQ fiber)
View(identify_outliers(data = df_l_ns, variable = "fibe_pk")) # alright, I'll remove 6003, 6053, 8031

View(identify_outliers(data = df_l_s, variable = "fibe_pk")) # 5048, 6032, 7043, 8058

# filter out le outliers
df_l_ns_out <- df_l_ns %>% filter(!subject_id %in% c(6053, 8031)) # woop
df_l_s_out <- df_l_s %>% filter(!subject_id %in% c(6032, 6091, 7077, 7116, 8085, 9035, 9056, 9065))

# smack em back together so you can run the models .. scree I'm gonna need to do this again for the others. 

df_l_out <- rbind(df_l_ns_out, df_l_s_out) # yee

# identify and remove outliers 
# out_c_ns <- boxplot.stats(df_l_ns$fibe_pk)$out # success! well..this shows the values
# df_out_c_ns <- which(df_l_ns$fibe_pk %in% c(out_c_ns)) screeee

# here's where we change the variable we're looking at (FFQ fiber)
View(identify_outliers(data = df_l_ns, variable = "dt_fibe_pk")) # alright, I'll remove 6003, 6053, 8031

View(identify_outliers(data = df_l_s, variable = "dt_fibe_pk")) # 5048, 6032, 7043, 8058

# filter out le outliers
df_l_ns_out <- df_l_ns %>% filter(!subject_id %in% c(6003, 6053, 8031)) # woop
df_l_s_out <- df_l_s %>% filter(!subject_id %in% c(5048, 6032, 7043, 7056, 7067, 8058, 9035))

# smack em back together so you can run the models .. scree I'm gonna need to do this again for the others. 

df_l_out <- rbind(df_l_ns_out, df_l_s_out) # yee


# LBP sol fib

# separating the two secretor status levels, to eliminate outliers from each
df_l_ns <- df_l[df_l$secr_status == "non_secretor", ]
df_l_s <- df_l[df_l$secr_status == "secretor", ]

# identify and remove outliers 
# out_c_ns <- boxplot.stats(df_l_ns$fibe_pk)$out # success! well..this shows the values
# df_out_c_ns <- which(df_l_ns$fibe_pk %in% c(out_c_ns)) screeee

# here's where we change the variable we're looking at (FFQ fiber)
View(identify_outliers(data = df_l_ns, variable = "dt_fiber_sol_pk")) # 

View(identify_outliers(data = df_l_s, variable = "dt_fiber_sol_pk")) # 

# filter out le outliers
df_l_ns_out <- df_l_ns %>% filter(!subject_id %in% c(6003)) # woop
df_l_s_out <- df_l_s %>% filter(!subject_id %in% c(5048, 6032, 9035))

# smack em back together so you can run the models .. scree I'm gonna need to do this again for the others. 

df_l_out <- rbind(df_l_ns_out, df_l_s_out) # yee

```

```{r lbp-add}

# LBP

mod_fibe_pk_l <- lm(lbp_ln ~ fibe_pk + secr_status + fibe_pk * secr_status + sex + bmi_final, data = df_l_out)
summary(mod_fibe_pk_l) # NS

# Plot with both genotypes 
# New facet label names for dose variable
secr.labs <- c("Non-secretors (n = 68)", "Secretors (n = 260)")
names(secr.labs) <- c("non_secretor", "secretor")

# Plot with both genotypes 

fut2fib_l1 <- ggplot(data = df_l_out, aes(x = fibe_pk, y = lbp_ln)) +
         geom_point(color = "black") +
        geom_smooth(method = "lm", 
                    se = T, 
                    color = "blue") +
  facet_grid(~secr_status,
        labeller = labeller(secr_status = secr.labs)) +
        labs(title = "LBP ~ Recent Fiber + Secretor Status + Recent Fiber * Secretor Status + Sex + BMI",
             x = "Recent Fiber Intake (grams/1000 kcal)",
             y = "Transformed LPS-binding protein (ln(x + 1))",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 18),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 16),
           axis.text = element_text(size = 14),
        legend.position = "none",
        plot.margin = margin(10, 50, 10, 30, unit = "pt"))

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_l1_out.jpg', plot = fut2fib_l1, device = 'jpeg', dpi = 300, width = 15, height = 6.25, units = "in")

#

mod_dt_fibe_pk_l <- lm(lbp_ln ~ dt_fibe_pk + secr_status + dt_fibe_pk * secr_status + sex + bmi_final, data = df_l_out)
summary(mod_dt_fibe_pk_l) # NS

# Plot with both genotypes 
# New facet label names for dose variable
secr.labs <- c("Non-secretors (n = 67)", "Secretors (n = 261)")
names(secr.labs) <- c("non_secretor", "secretor")

# Adding a label for statistical analysis results 
analysis_results <- "Secretor Status: β = -0.40, P = 0.07, \n Interaction (Fiber:Secretor Status): β = 0.03, P = 0.11"

# Add a new column to indicate whether each observation belongs to the facet you want to label
df_l_out$facet_label <- ifelse(df_l_out$secr_status == "secretor", TRUE, FALSE)


# Plot with both genotypes 

fut2fib_l2 <- ggplot(data = df_l_out, aes(x = dt_fibe_pk, y = lbp_ln)) +
         geom_point(color = "black") +
        geom_smooth(method = "lm", 
                    se = T, 
                    color = "blue") +
  facet_grid(~secr_status,
        labeller = labeller(secr_status = secr.labs)) +
        labs(title = "LBP ~ Habitual Fiber + Secretor Status + Habitual Fiber * Secretor Status + Sex + BMI",
             x = "Habitual Fiber Intake (grams/1000 kcal)",
             y = "Transformed LPS-binding protein (ln(x + 1))",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 18),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 16),
           axis.text = element_text(size = 14),
        legend.position = "none",
        plot.margin = margin(10, 50, 10, 30, unit = "pt")) + 
 geom_text(data = subset(df_l_out, facet_label == TRUE), aes(x = 10, y = 4, label = analysis_results), size = 4.5, color = "black", hjust = 0)

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_l2_out.jpg', plot = fut2fib_l2, device = 'jpeg', dpi = 300, width = 15, height = 6.25, units = "in")


# LBP

mod_dt_fiber_sol_pk_l <- lm(lbp_ln ~ dt_fiber_sol_pk + secr_status + dt_fiber_sol_pk * secr_status + sex + bmi_final, data = df_l_out)
summary(mod_dt_fiber_sol_pk_l) # NS

# Plot with both genotypes 
# New facet label names for dose variable
secr.labs <- c("Non-secretors (n = 69)", "Secretors (n = 265)")
names(secr.labs) <- c("non_secretor", "secretor")

# Adding a label for statistical analysis results 
analysis_results <- "Secretor Status: β = -0.33, P = 0.10, \n Interaction (Fiber:Secretor Status): β = 0.08, P = 0.16"

# Add a new column to indicate whether each observation belongs to the facet you want to label
df_l_out$facet_label <- ifelse(df_l_out$secr_status == "secretor", TRUE, FALSE)

# Plot with both genotypes 

fut2fib_l3 <- ggplot(data = df_l_out, aes(x = dt_fiber_sol_pk, y = lbp_ln)) +
                geom_point(color = "black") +
        geom_smooth(method = "lm", 
                    se = T, 
                    color = "blue") +
  facet_grid(~secr_status,
        labeller = labeller(secr_status = secr.labs)) +
        labs(title = "LBP ~ Habitual Soluble Fiber + Secretor Status + Hab. Soluble Fiber * Secretor Status + Sex + BMI",
             x = "Habitual Soluble Fiber Intake (grams/1000 kcal)",
             y = "Transformed LBP (ln(x + 1))",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 18),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 16),
           axis.text = element_text(size = 14),
        legend.position = "none",
        plot.margin = margin(10, 50, 10, 30, unit = "pt")) + 
 geom_text(data = subset(df_l_out, facet_label == TRUE), aes(x = 3, y = 4, label = analysis_results), size = 4.5, color = "black", hjust = 0)

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_l3_out.jpg', plot = fut2fib_l3, device = 'jpeg', dpi = 300, width = 15, height = 6.25, units = "in")

```

