---
title: "FUT2_dietguthealth_fiber"
author: "Yasmine"
date: "`r Sys.Date()`"
output: html_document
---

Purpose: determine associations between secretor status, fiber intake and GI inflammation marker levels. and PLOT

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(ggpubr)

```

```{r import}

# Genotyping 
fut2 <- read.csv("/Users/yasmine.bouzid/Documents/FUT2_analysis/data/forR_fut2.csv", header = T)

# Gut health 
df_c <- read.csv("/Users/yasmine.bouzid/Documents/GitHub/diet_guthealth/data/df_c.csv", header = T)

df_m <- read.csv("/Users/yasmine.bouzid/Documents/GitHub/diet_guthealth/data/df_m.csv", header = T)

df_n <- read.csv("/Users/yasmine.bouzid/Documents/GitHub/diet_guthealth/data/df_n.csv", header = T)

df_l <- read.csv("/Users/yasmine.bouzid/Documents/GitHub/diet_guthealth/data/df_l.csv", header = T)

# MEEEERGE 

df_c <- merge(df_c, fut2, by = "subject_id") # n = 288
df_m <- merge(df_m, fut2, by = "subject_id") # n = 288
df_n <- merge(df_n, fut2, by = "subject_id") # n = 282
df_l <- merge(df_l, fut2, by = "subject_id") # n = 338

# unfortunately, need to correct structure of some variables each time -->

df_c$subject_id <- as.factor(as.character(df_c$subject_id))
df_c$sex <- df_c$sex %>% recode_factor('1' = 'Male', '2' = "Female")
df_c$age_cat <- df_c$age_cat %>% recode_factor('1' = '18-33.99 years', '2' = "34-49.99 years", '3' = "50-65 years")
df_c$bmi_cat <- df_c$bmi_cat %>% recode_factor('1' = 'Normal', '2' = "Overweight", '3' = "Obese")
df_c$secr_status <- as.factor(as.character(df_c$secr_status))

df_m$subject_id <- as.factor(as.character(df_m$subject_id))
df_m$sex <- df_m$sex %>% recode_factor('1' = 'Male', '2' = "Female")
df_m$age_cat <- df_m$age_cat %>% recode_factor('1' = '18-33.99 years', '2' = "34-49.99 years", '3' = "50-65 years")
df_m$bmi_cat <- df_m$bmi_cat %>% recode_factor('1' = 'Normal', '2' = "Overweight", '3' = "Obese")
df_m$secr_status <- as.factor(as.character(df_m$secr_status))

df_n$subject_id <- as.factor(as.character(df_n$subject_id))
df_n$sex <- df_n$sex %>% recode_factor('1' = 'Male', '2' = "Female")
df_n$age_cat <- df_n$age_cat %>% recode_factor('1' = '18-33.99 years', '2' = "34-49.99 years", '3' = "50-65 years")
df_n$bmi_cat <- df_n$bmi_cat %>% recode_factor('1' = 'Normal', '2' = "Overweight", '3' = "Obese")
df_n$secr_status <- as.factor(as.character(df_n$secr_status))

df_l$subject_id <- as.factor(as.character(df_l$subject_id))
df_l$sex <- df_l$sex %>% recode_factor('1' = 'Male', '2' = "Female")
df_l$age_cat <- df_l$age_cat %>% recode_factor('1' = '18-33.99 years', '2' = "34-49.99 years", '3' = "50-65 years")
df_l$bmi_cat <- df_l$bmi_cat %>% recode_factor('1' = 'Normal', '2' = "Overweight", '3' = "Obese")
df_l$secr_status <- as.factor(as.character(df_l$secr_status))

```

Models used for analysis: regression of transformed GI inflammation marker ~ dietary component
Note: Age, sex, BMI not included as covariates because not significantly associated with calprotectin and MPO levels. Sex included for neopterin outcome. Sex and BMI included for LBP outcome. Associations previously established. 

GIM ~ fiber + FUT2 + fiber:FUT2 + age + sex + BMI

```{r asa24-total-fiber}

# Create fibe_pk (pk = per 1000 kcal)

df_c$fibe_pk <- df_c$fibe/(df_c$kcal/1000)
df_m$fibe_pk <- df_m$fibe/(df_m$kcal/1000)
df_n$fibe_pk <- df_n$fibe/(df_n$kcal/1000)
df_l$fibe_pk <- df_l$fibe/(df_l$kcal/1000)

# Calprotectin

mod_fibe_pk_c <- lm(clpn_ln ~ fibe_pk + secr_status + fibe_pk * secr_status, data = df_c)
summary(mod_fibe_pk_c) # 

# Plot with both genotypes 
# New facet label names for dose variable
secr.labs <- c("Non-secretors (n = 60)", "Secretors (n = 228)")
names(secr.labs) <- c("non_secretor", "secretor")

# Adding a label for statistical analysis results 
analysis_results <- "Secretor Status: β = 0.82, P = 0.02, \n Interaction (Fiber:Secretor Status): β = -0.07, P = 0.02"

# Add a new column to indicate whether each observation belongs to the facet you want to label
df_c$facet_label <- ifelse(df_c$secr_status == "secretor", TRUE, FALSE)

#annotations <- data.frame(
 # x = c(30),  # X coordinate for the annotation
  #y = c(6),   # Y coordinate for the annotation
#  label = analysis_results  # Text label for the annotation
#)

fut2fib_c1 <- ggplot(data = df_c, aes(x = fibe_pk, y = clpn_ln)) +
        geom_point(color = "black") +
        geom_smooth(method = "lm", 
                    se = T, 
                    color = "blue") +
  facet_grid(~secr_status,
             labeller = labeller(secr_status = secr.labs)) +
        labs(title = "Calprotectin ~ Recent Fiber + Secretor Status + Recent Fiber * Secretor Status",
             x = "Recent Fiber Intake (grams/1000 kcal)",
             y = "Transformed Calprotectin (ln(x + 3))",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 18),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 16),
           axis.text = element_text(size = 14),
        legend.position = "none",
        plot.margin = margin(10, 50, 10, 30, unit = "pt")) + 
 geom_text(data = subset(df_c, facet_label == TRUE), aes(x = 13, y = 6.5, label = analysis_results), size = 4.5, color = "black", hjust = 0)


ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_c1.jpg', plot = fut2fib_c1, device = 'jpeg', dpi = 300, width = 15, height = 6.25, units = "in")

# Myeloperoxidase

mod_fibe_pk_m <- lm(mpo_ln ~ fibe_pk + secr_status+ fibe_pk * secr_status, data = df_m)
summary(mod_fibe_pk_m) # 


df_m$secr_status <- as.factor(as.character(df_m$secr_status))

# Plot with both genotypes 

fut2fib_m1 <- ggplot(data = df_m, aes(x = fibe_pk, y = mpo_ln)) +
        geom_point(aes(color = factor(secr_status))) +
        geom_smooth(method = "lm", 
                    se = T, 
                    aes(color = factor(secr_status))) +
  facet_grid(~secr_status) +
        labs(title = "Fiber Intake vs. Myeloperoxidase by Secretor Status",
             x = "Recent Fiber Intake (grams/1000 kcal)",
             y = "Transformed Myeloperoxidase (ln(x + 1))",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 20),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 18),
           axis.text = element_text(size = 15),
        plot.margin = margin(10, 50, 10, 30, unit = "pt"))

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_m1.jpg', plot = fut2fib_m1, device = 'jpeg', dpi = 300, width = 21, height = 7, units = "in")


# Neopterin

mod_fibe_pk_n <- lm(nptn_boxcox ~ fibe_pk + secr_status + fibe_pk * secr_status + sex, data = df_n)
summary(mod_fibe_pk_n) #

df_n$secr_status <- as.factor(as.character(df_n$secr_status))

# Plot with both genotypes 

fut2fib_n1 <- ggplot(data = df_n, aes(x = fibe_pk, y = nptn_boxcox)) +
        geom_point(aes(color = factor(secr_status))) +
        geom_smooth(method = "lm", 
                    se = T, 
                    aes(color = factor(secr_status))) +
  facet_grid(~secr_status) +
        labs(title = "Fiber Intake vs. Neopterin by Secretor Status",
             x = "Recent Fiber Intake (grams/1000 kcal)",
             y = "Transformed Neopterin (Box Cox)",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 20),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 18),
           axis.text = element_text(size = 15),
        plot.margin = margin(10, 50, 10, 30, unit = "pt"))

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_n1.jpg', plot = fut2fib_n1, device = 'jpeg', dpi = 300, width = 21, height = 7, units = "in")


# LBP

mod_fibe_pk_l <- lm(lbp_ln ~ fibe_pk + secr_status + fibe_pk * secr_status + sex + bmi_final, data = df_l)
summary(mod_fibe_pk_l) # 

df_l$secr_status <- as.factor(as.character(df_l$secr_status))

# Plot with both genotypes 
# New facet label names for dose variable
secr.labs <- c("Non-secretors (n = 70)", "Secretors (n = 268)")
names(secr.labs) <- c("non_secretor", "secretor")

# Adding a label for statistical analysis results 
# analysis_results <- "Secretor Status: β = -0.03, P = 0.01, \n Interaction (Fiber:Secretor Status): β = 0.04, P = 0.02"

# Add a new column to indicate whether each observation belongs to the facet you want to label
# df_l$facet_label <- ifelse(df_l$secr_status == "secretor", TRUE, FALSE)

# Plot with both genotypes 

fut2fib_l1 <- ggplot(data = df_l, aes(x = fibe_pk, y = lbp_ln)) +
        geom_point(color = "black") +
        geom_smooth(method = "lm", 
                    se = T, 
                    color = "blue") +
  facet_grid(~secr_status,
        labeller = labeller(secr_status = secr.labs)) +
        labs(title = "LBP ~ Recent Fiber + Secretor Status + Recent Fiber * Secretor Status + Sex + BMI",
             x = "Recent Fiber Intake (grams/1000 kcal)",
             y = "Transformed LPS-binding protein (ln(x + 1))",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 18),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 16),
           axis.text = element_text(size = 14),
        legend.position = "none",
        plot.margin = margin(10, 50, 10, 30, unit = "pt")) # + 
 # geom_text(data = subset(df_l, facet_label == TRUE), aes(x = 10, y = 4, label = analysis_results), size = 4.5, color = "black", hjust = 0)

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_l1.jpg', plot = fut2fib_l1, device = 'jpeg', dpi = 300, width = 15, height = 6.25, units = "in")


```
Next, we'll look at total fiber from FFQ (dt_fibe)

```{r ffq-total-fiber}

# Create dt_fibe_pk (pk = per 1000 kcal)

df_c$dt_fibe_pk <- df_c$dt_fibe/(df_c$dt_kcal/1000)
df_m$dt_fibe_pk <- df_m$dt_fibe/(df_m$dt_kcal/1000)
df_n$dt_fibe_pk <- df_n$dt_fibe/(df_n$dt_kcal/1000)
df_l$dt_fibe_pk <- df_l$dt_fibe/(df_l$dt_kcal/1000)

# Calprotectin

mod_dt_fibe_pk_c <- lm(clpn_ln ~ dt_fibe_pk + secr_status + dt_fibe_pk * secr_status, data = df_c)
summary(mod_dt_fibe_pk_c) # NS

# Plot with both genotypes 
# New facet label names for dose variable
secr.labs <- c("Non-secretors (n = 60)", "Secretors (n = 228)")
names(secr.labs) <- c("non_secretor", "secretor")

# Adding a label for statistical analysis results 
analysis_results <- "Secretor Status: β = 1.17, P = 0.008, \n Interaction (Fiber:Secretor Status): β = -0.09, P = 0.005"

# Add a new column to indicate whether each observation belongs to the facet you want to label
df_c$facet_label <- ifelse(df_c$secr_status == "secretor", TRUE, FALSE)

# Plot with both genotypes 

fut2fib_c2 <- ggplot(data = df_c, aes(x = dt_fibe_pk, y = clpn_ln)) +
        geom_point(color = "black") +
        geom_smooth(method = "lm", 
                    se = T, 
                    color = "blue") +
  facet_grid(~secr_status,
        labeller = labeller(secr_status = secr.labs)) +
        labs(title = "Calprotectin ~ Habitual Fiber + Secretor Status + Habitual Fiber * Secretor Status",
             x = "Habitual Fiber Intake (grams/1000 kcal)",
             y = "Transformed Calprotectin (ln(x + 3))",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 18),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 16),
           axis.text = element_text(size = 14),
        legend.position = "none",
        plot.margin = margin(10, 50, 10, 30, unit = "pt")) + 
 geom_text(data = subset(df_c, facet_label == TRUE), aes(x = 10, y = 6.5, label = analysis_results), size = 4.5, color = "black", hjust = 0)

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_c2.jpg', plot = fut2fib_c2, device = 'jpeg', dpi = 300, width = 15, height = 6.25, units = "in")

# Myeloperoxidase

mod_dt_fibe_pk_m <- lm(mpo_ln ~ dt_fibe_pk + secr_status + dt_fibe_pk * secr_status, data = df_m)
summary(mod_dt_fibe_pk_m) # NS


# Plot with both genotypes 

fut2fib_m2 <- ggplot(data = df_m, aes(x = dt_fibe_pk, y = mpo_ln)) +
        geom_point(aes(color = factor(secr_status))) +
        geom_smooth(method = "lm", 
                    se = T, 
                    aes(color = factor(secr_status))) +
  facet_grid(~secr_status) +
        labs(title = "Fiber Intake vs. Myeloperoxidase by Secretor Status",
             x = "Habitual Fiber Intake (grams/1000 kcal)",
             y = "Transformed Myeloperoxidase (ln(x + 1))",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 20),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 18),
           axis.text = element_text(size = 15),
        plot.margin = margin(10, 50, 10, 30, unit = "pt"))

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_m2.jpg', plot = fut2fib_m2, device = 'jpeg', dpi = 300, width = 21, height = 7, units = "in")

# Neopterin

mod_dt_fibe_pk_n <- lm(nptn_boxcox ~ dt_fibe_pk + secr_status + dt_fibe_pk * secr_status + sex, data = df_n)
summary(mod_dt_fibe_pk_n) # NS

# Plot with both genotypes 

fut2fib_n2 <- ggplot(data = df_n, aes(x = dt_fibe_pk, y = nptn_boxcox)) +
        geom_point(aes(color = factor(secr_status))) +
        geom_smooth(method = "lm", 
                    se = T, 
                    aes(color = factor(secr_status))) +
  facet_grid(~secr_status) +
        labs(title = "Fiber Intake vs. Neopterin by Secretor Status",
             x = "Habitual Fiber Intake (grams/1000 kcal)",
             y = "Transformed Neopterin (Box Cox)",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 20),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 18),
           axis.text = element_text(size = 15),
        plot.margin = margin(10, 50, 10, 30, unit = "pt"))

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_n2.jpg', plot = fut2fib_n2, device = 'jpeg', dpi = 300, width = 21, height = 7, units = "in")


# LBP

mod_dt_fibe_pk_l <- lm(lbp_ln ~ dt_fibe_pk + secr_status + dt_fibe_pk * secr_status + sex + bmi_final, data = df_l)
summary(mod_dt_fibe_pk_l) # NS

# Plot with both genotypes 
# New facet label names for dose variable
secr.labs <- c("Non-secretors (n = 70)", "Secretors (n = 268)")
names(secr.labs) <- c("non_secretor", "secretor")

# Adding a label for statistical analysis results 
analysis_results <- "Secretor Status: β = -0.03, P = 0.01, \n Interaction (Fiber:Secretor Status): β = 0.04, P = 0.02"

# Add a new column to indicate whether each observation belongs to the facet you want to label
df_l$facet_label <- ifelse(df_l$secr_status == "secretor", TRUE, FALSE)


# Plot with both genotypes 

fut2fib_l2 <- ggplot(data = df_l, aes(x = dt_fibe_pk, y = lbp_ln)) +
         geom_point(color = "black") +
        geom_smooth(method = "lm", 
                    se = T, 
                    color = "blue") +
  facet_grid(~secr_status,
        labeller = labeller(secr_status = secr.labs)) +
        labs(title = "LBP ~ Habitual Fiber + Secretor Status + Habitual Fiber * Secretor Status + Sex + BMI",
             x = "Habitual Fiber Intake (grams/1000 kcal)",
             y = "Transformed LPS-binding protein (ln(x + 1))",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 18),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 16),
           axis.text = element_text(size = 14),
        legend.position = "none",
        plot.margin = margin(10, 50, 10, 30, unit = "pt")) + 
 geom_text(data = subset(df_l, facet_label == TRUE), aes(x = 10, y = 4, label = analysis_results), size = 4.5, color = "black", hjust = 0)

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_l2.jpg', plot = fut2fib_l2, device = 'jpeg', dpi = 300, width = 15, height = 6.25, units = "in")



```

Last, we'll look at soluble fiber from the FFQ (dt_fiber_sol)

```{r ffq-sol-fiber}


# Create dt_fiber_sol_pk (pk = per 1000 kcal)

df_c$dt_fiber_sol_pk <- df_c$dt_fiber_sol/(df_c$dt_kcal/1000)
df_m$dt_fiber_sol_pk <- df_m$dt_fiber_sol/(df_m$dt_kcal/1000)
df_n$dt_fiber_sol_pk <- df_n$dt_fiber_sol/(df_n$dt_kcal/1000)
df_l$dt_fiber_sol_pk <- df_l$dt_fiber_sol/(df_l$dt_kcal/1000)

# Calprotectin

mod_dt_fiber_sol_pk_c <- lm(clpn_ln ~ dt_fiber_sol_pk + secr_status + dt_fiber_sol_pk * secr_status, data = df_c)
summary(mod_dt_fiber_sol_pk_c) #

# Plot with both genotypes 
# New facet label names for dose variable
secr.labs <- c("Non-secretors (n = 60)", "Secretors (n = 228)")
names(secr.labs) <- c("non_secretor", "secretor")

# Adding a label for statistical analysis results 
analysis_results <- "Secretor Status: β = 1.04, P = 0.02, \n Interaction (Fiber:Secretor Status): β = -0.31, P = 0.02"

# Add a new column to indicate whether each observation belongs to the facet you want to label
df_c$facet_label <- ifelse(df_c$secr_status == "secretor", TRUE, FALSE)

# Plot with both genotypes 

fut2fib_c3 <- ggplot(data = df_c, aes(x = dt_fiber_sol_pk, y = clpn_ln)) +
        geom_point(color = "black") +
        geom_smooth(method = "lm", 
                    se = T, 
                    color = "blue") +
  facet_grid(~secr_status,
        labeller = labeller(secr_status = secr.labs)) +
        labs(title = "Calprotectin ~ Habitual Soluble Fiber + Secretor Status + Habitual Sol. Fiber * Secretor Status",
             x = "Habitual Soluble Fiber Intake (grams/1000 kcal)",
             y = "Transformed Calprotectin (ln(x + 3))",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 18),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 16),
           axis.text = element_text(size = 14),
        legend.position = "none",
        plot.margin = margin(10, 50, 10, 30, unit = "pt")) + 
 geom_text(data = subset(df_c, facet_label == TRUE), aes(x = 3, y = 6.5, label = analysis_results), size = 4.5, color = "black", hjust = 0)

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_c3.jpg', plot = fut2fib_c3, device = 'jpeg', dpi = 300, width = 15, height = 6.25, units = "in")

# Myeloperoxidase

mod_dt_fiber_sol_pk_m <- lm(mpo_ln ~ dt_fiber_sol_pk + secr_status + dt_fiber_sol_pk * secr_status, data = df_m)
summary(mod_dt_fiber_sol_pk_m) # 

# Plot with both genotypes 
# New facet label names for dose variable
secr.labs <- c("Non-secretors (n = 60)", "Secretors (n = 228)")
names(secr.labs) <- c("non_secretor", "secretor")

# Adding a label for statistical analysis results 
analysis_results <- "Secretor Status: β = 0.85, P = 0.02, \n Interaction (Fiber:Secretor Status): β = -0.23, P = 0.03"

# Add a new column to indicate whether each observation belongs to the facet you want to label
df_m$facet_label <- ifelse(df_m$secr_status == "secretor", TRUE, FALSE)

# Plot with both genotypes 

fut2fib_m3 <- ggplot(data = df_m, aes(x = dt_fiber_sol_pk, y = mpo_ln)) +
           geom_point(color = "black") +
        geom_smooth(method = "lm", 
                    se = T, 
                    color = "blue") +
  facet_grid(~secr_status,
        labeller = labeller(secr_status = secr.labs)) +
        labs(title = "Myeloperoxidase ~ Habitual Soluble Fiber + Secretor Status + Habitual Sol. Fiber * Secretor Status",
             x = "Habitual Soluble Fiber Intake (grams/1000 kcal)",
             y = "Transformed Myeloperoxidase (ln(x + 1))",
             fill = "Secretor Status") +
  theme_bw() + 
theme(text = element_text(size = 18),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 16),
           axis.text = element_text(size = 14),
        legend.position = "none",
        plot.margin = margin(10, 50, 10, 30, unit = "pt")) + 
 geom_text(data = subset(df_c, facet_label == TRUE), aes(x = 5, y = 8, label = analysis_results), size = 4.5, color = "black", hjust = 0)

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_m3.jpg', plot = fut2fib_m3, device = 'jpeg', dpi = 300, width = 15, height = 6.25, units = "in")

# Neopterin

mod_dt_fiber_sol_pk_n <- lm(nptn_boxcox ~ dt_fiber_sol_pk + secr_status + dt_fiber_sol_pk * secr_status + sex, data = df_n)
summary(mod_dt_fiber_sol_pk_n) # NS

# Plot with both genotypes 

fut2fib_n3 <- ggplot(data = df_n, aes(x = dt_fiber_sol_pk, y = nptn_boxcox)) +
        geom_point(aes(color = factor(secr_status))) +
        geom_smooth(method = "lm", 
                    se = T, 
                    aes(color = factor(secr_status))) +
  facet_grid(~secr_status) +
        labs(title = "Fiber Intake vs. Neopterin by Secretor Status",
             x = "Habitual Soluble Fiber Intake (grams/1000 kcal)",
             y = "Transformed Neopterin (Box Cox)",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 20),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 18),
           axis.text = element_text(size = 15),
        plot.margin = margin(10, 50, 10, 30, unit = "pt"))

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_n3.jpg', plot = fut2fib_n3, device = 'jpeg', dpi = 300, width = 21, height = 7, units = "in")

# LBP

mod_dt_fiber_sol_pk_l <- lm(lbp_ln ~ dt_fiber_sol_pk + secr_status + dt_fiber_sol_pk * secr_status + sex + bmi_final, data = df_l)
summary(mod_dt_fiber_sol_pk_l) # NS

# Plot with both genotypes 
# New facet label names for dose variable
secr.labs <- c("Non-secretors (n = 70)", "Secretors (n = 268)")
names(secr.labs) <- c("non_secretor", "secretor")

# Adding a label for statistical analysis results 
analysis_results <- "Secretor Status: β = -0.46, P = 0.02, \n Interaction (Fiber:Secretor Status): β = 0.13, P = 0.02"

# Add a new column to indicate whether each observation belongs to the facet you want to label
df_l$facet_label <- ifelse(df_l$secr_status == "secretor", TRUE, FALSE)

# Plot with both genotypes 

fut2fib_l3 <- ggplot(data = df_l, aes(x = dt_fiber_sol_pk, y = lbp_ln)) +
                geom_point(color = "black") +
        geom_smooth(method = "lm", 
                    se = T, 
                    color = "blue") +
  facet_grid(~secr_status,
        labeller = labeller(secr_status = secr.labs)) +
        labs(title = "LBP ~ Habitual Soluble Fiber + Secretor Status + Hab. Soluble Fiber * Secretor Status + Sex + BMI",
             x = "Habitual Soluble Fiber Intake (grams/1000 kcal)",
             y = "Transformed LBP (ln(x + 1))",
             fill = "Secretor Status") +
  theme_bw() + 
  theme(text = element_text(size = 18),
        plot.title = element_text(size = 20),
           axis.title = element_text(size = 16),
           axis.text = element_text(size = 14),
        legend.position = "none",
        plot.margin = margin(10, 50, 10, 30, unit = "pt")) + 
 geom_text(data = subset(df_l, facet_label == TRUE), aes(x = 3, y = 4, label = analysis_results), size = 4.5, color = "black", hjust = 0)

ggsave(filename = '/Users/yasmine.bouzid/Documents/FUT2_analysis/plots/fut2fib_l3.jpg', plot = fut2fib_l3, device = 'jpeg', dpi = 300, width = 15, height = 6.25, units = "in")


```

**Summary of Findings**: 

1. Recent fiber intake: For calprotectin model, secretor status significant and interaction between fiber and secretor status significant 
2. Habitual fiber intake: same as above 
3. Habitual soluble fiber intake: for BOTH clpn and MPO, secretor status significant and interaction between fiber and secretor status significant 
